Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola

### 2022-07-19 Manuscript/main.tex
Worked on partial plots

All component GLMMs of the pSEM were written in Stan 2.18.1 \citep{gelman2015} and run using \texttt{rstan} 2.26.13.
We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
Four separate chains were run with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
% This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
% However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
% p-values listed below (also in Tables S3 and S4) are \textit{posterior} p-values, representing the proportion of the posterior distribution that overlapped zero, with Z-scores (mean/standard deviation of posterior) showing the effect size.
% Predictions from models are median values of the posterior, representing the median prediction, while intervals displayed in figures are credible intervals (CIs), representing 95\% of the samples drawn from the posterior distribution (analogous to confidence intervals, see \citealt{gelman2013}).

@@

% %This could probably be reduced to a blurb
% Plant size and pollen deposition were the main drivers of yield in seed canola, while plant size was the main driver of yield in commodity canola.
% Distance from the field edge had a negative effect on honey bee visitation in both commodity and seed canola (Z=-3.7, -2.5, respectively), and unexpectedly, had a negative effect on leafcutter bee visitation (Z= -4.4), showing that overall visitation decreases with distance into the field.
% The path from leafcutter bee visitation to pollen deposition was strong in seed canola (Z=3.2), but there was no path from honey bee visitation to pollen deposition in either crop type.
% Pollen deposition increased pod set (Z=3.1) and seeds per pod (Z=2.3) in seed canola, but was not present in commodity canola, showing that yield in seed canola, but not commodity canola, is strongly dependent on pollination.
% %The path from seeds per pod to weight per seed was negative in seed canola (Z=-15.0) but positive in commodity canola (Z=6.1) 
% Both crop types had strong negative paths from flower survival to flowers per plant (commodity Z=-12.5, seed Z=-12.1), indicating that high flower survival suppressed future flower production.
% Commodity canola had a similar weight per seed, regardless of the plant size, but in seed canola, plant size had a strong influence on seeds per pod (Z=5.6) and weight per seed (4.6).
% Finally, in both crop types, the paths leading from plant size were the dominant signal influencing pod set (commodity Z=5.8; seed Z=19.9), but the path from pollen deposition to pod set was only present in seed canola, showing that plant resources matter strongly for both crop types, but that increased pollen deposition only benefits seed canola.
% 
% The results of the underlying components of each pSEM are shown in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}:
% 
% \begin{table}
% \centering
% \caption{Summary of main measured variables. Vegetative mass refers to the non-seed plant mass.}
% \begin{tabular}{r|llllll|llllll}
%                                        & \multicolumn{6}{l|}{Commodity Fields}           & \multicolumn{6}{l}{Seed Fields}                    \\
% Parameter                              & Min  & Median & Mean   & Max   & SD     & N    & Min    & Median & Mean   & Max    & SD     & N     \\ \hline
% Honey bee visitation (per min)      & 0    & 0      & 0.17   & 3.64  & 0.48   & 271  & 0      & 2      & 14.15  & 215    & 25.13  & 665   \\
% Leafcutter bee visitation (per min) & -    & -      & -      & -     & -      & -    & 0      & 2      & 13.93  & 212    & 25.49  & 665   \\
% Pollen (\# per stigma)                 & 0    & 155    & 293.32 & 3891  & 385.04 & 1355 & 0      & 7      & 21.76  & 578    & 42.53  & 1080  \\
% Flowers per plant                      & 13   & 157    & 196.05 & 1094  & 150.87 & 789  & 26     & 362.50 & 461.33 & 2712   & 326.59 & 600   \\
% Pods per plant                         & 5    & 112    & 143.17 & 892   & 114.57 & 789  & 10     & 244.50 & 299.41 & 1410   & 207.68 & 600   \\
% Seeds per pod                          & 4.6  & 23.6   & 22.95  & 35.4  & 4.97   & 789  & 1.8    & 16.6   & 16.40  & 30.60  & 5.52   & 600   \\
% Weight per 1000 seeds (g)              & 0.39 & 2.72   & 2.74   & 5.35  & 0.8    & 789  & 1.04   & 3.42   & 3.43   & 5.59   & 0.88   & 600  \\
% Total vegetative mass (g)                    & 0.77 & 14.29  & 18.19  & 110.2 & 14.41  & 789  & 1.1849 & 25.20  & 30.32  & 144.32 & 21.16  & 600   \\
% Total seed mass (g)                          & 0.01 & 5.46   & 6.87   & 47.9  & 5.97   & 789  & 0.02   & 7.54   & 9.50   & 60.77  & 7.90   & 600   
% \end{tabular}
% \end{table}

>>>>

All component GLMMs of the pSEM were written in Stan 2.18.1 \citep{gelman2015} and run using \texttt{rstan} 2.26.13.
We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
Four separate chains were run with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
p-values listed below (also in Tables S3 and S4) are \textit{posterior} p-values, representing the proportion of the posterior distribution that overlapped zero, with Z-scores (mean/standard deviation of posterior) showing the effect size.
% This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
% However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
% Predictions from models are median values of the posterior, representing the median prediction, while intervals displayed in figures are credible intervals (CIs), representing 95\% of the samples drawn from the posterior distribution (analogous to confidence intervals, see \citealt{gelman2013}).

@@

\subsection{Overall path analysis}

Plant size and pollen deposition were the main drivers of seed production in seed canola, while plant size was the main driver in commodity canola (see Figure \ref{fig:allSEM} for paths and effect sizes). 
HB visitation decreased with distance from the edge of the field in both commodity and seed canola; unexpectedly, LCB visitation also decreased with distance from the edge of the field in seed fields.
LCB visitation strongly increased pollen deposition was strong in seed canola, but there was no strong effect of HB visitation in either crop type.
Both crop types had strong negative paths from pods per plant to flowers per plant, indicating that high flower survival suppressed future flower production.
Plant size increased the number of seeds per pod in both crop types, and also increased seed size in seed canola plants.
Finally, pollen deposition increased pod set and seeds per pod in seed canola, but did not affect seed or pod production in commodity canola, showing that plant resources matter strongly for both crops, but that increased pollen only benefits seed canola crops.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allSEM.png}
    \caption{Results of path analysis in commodity and seed fields. The width of each arrow is proportional to the effect size of each component path (number also displayed). Transparent arrows show path coefficients whose 95 posterior intervals overlapped zero.}
    \label{fig:allSEM}
\end{figure}
